How hunting experience, habitat structure, and prey predictability jointly shape individual specialisation in predator foraging mode in an online videogame

### 2021-05-20 manuscript/Chapter3-manuscript.Rmd
notes intro
updated intro

Several studies have often shown that generalist and specialist individuals don't differ in fitness related measures [sources: à partir de Woo]. An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc]. The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns. The rationale behind this prediction is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique as it is easier to assess prey predictability over shorter time-scales. In contrast, individual generalists should be advantaged over longer time scales as resource parameters are expected to fluctuate.

@@

A second important driver of individual differences in predator hunting behaviour is related to habitat specific features [sources]. Predators are expected to adjust their foraging strategies to their habitat as they offer different structures which can aid/impair (ex. perches, vegetation density) vision or the ability to hide, which may facilitate the use of a specific hunting mode (ambush vs cursorial). For instance, predators often shift from a cursorial hunting mode in open and homogeneous landscapes, to an ambush hunting mode in closed and heterogeneous landscapes [sources].

>>>>

A number of long-term studies have observed similar fitness related measures generalist and specialist individuals [sources: à partir de Woo]. An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc]. The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns. The rationale behind this prediction is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique as it is easier to assess prey predictability over shorter time-scales. In contrast, individual generalists should be advantaged over longer time scales as resource parameters are expected to fluctuate.

@@

A second important driver of individual differences in predator hunting behaviour is related to habitat-specific features [sources, Kobler, parler de la ideal free distribution?]. Predators are expected to adjust their foraging mode (ambush vs cursorial) to habitat structures that aid/impair (ex. perches, vegetation density) their vision, ability to hide, or energetic/time requirements. For instance, predators who ambush in closed and heterogeneous landscapes often switch to cursorial hunters in open and homogeneous landscapes [sources]. (Donner exemple des orcs)
